Peer Assessment 1
=================


Loading and preprocessing the data
----------------------------------

```{r echo = TRUE}
unzip("activity.zip")
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date, "%Y-%m-%d")
```
What is mean total number of steps taken per day?
-------------------------------------------------

Make a histogram of the total number of steps taken each day

```{r echo = TRUE}
table <- aggregate(activity$steps~activity$date,data=activity,FUN=sum)
colnames(table) <- c("date","steps")

Sys.setlocale(locale = "C")
plot(steps ~ date, table, type="h")
```

The mean and median total number of steps taken per day

```{r echo = TRUE}
mean(table$steps)
median(table$steps)
```
What is the average daily activity pattern?
-------------------------------------------

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r echo = TRUE}
table2 <- aggregate(activity$steps~activity$interval,data=activity,FUN=mean)
colnames(table2) <- c("interval","steps")
plot(steps ~ interval, table2, type="l")
```


Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r echo = TRUE}
table2$interval[table2$steps == max(table2$steps)]
```

Imputing missing values
-----------------------

The total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r echo = TRUE}
na_num <- 0
for (i in 1:nrow(activity)){
        
        if(is.na(activity[i,1])) {na_num <- (na_num +1)}
        
}

print(na_num)
```

The strategy for filling in the missing values in the dataset is the mean for that 5-minute interval.

```{r echo = TRUE}

activityNew <- activity

for (i in 1:nrow(activityNew)){
        if (is.na(activityNew[i,1])) activityNew[i,1]<-table2[table2[1]==activityNew[i,3]][2]
        
}
```
activityNew is a new data set without missing values

The histogram of the total number of steps taken each day

```{r echo = TRUE}
totalsteps <- aggregate(activityNew$steps~activityNew$date,data=activityNew,FUN=sum)
colnames(totalsteps) <- c("date","steps")
plot(steps ~ date, totalsteps, type="h")
```

The mean and median total number of steps taken per day

```{r echo = TRUE}
 
mean(totalsteps$steps)
median(totalsteps$steps)
```

Are there differences in activity patterns between weekdays and weekends?
-------------------------------------------------------------------------

Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r echo = TRUE}
wd <- activity$date
wd <- strptime(wd, "%Y-%m-%d")
wd <- weekdays(wd)
wd <- as.character(wd)

for (i in 1:length(wd)){
        if(wd[i]=="Saturday" | wd[i]=="Sunday") {
                wd[i] <- "weekend"
        } else {
                wd[i] <- "weekday"
        }
}
wd <- factor(wd)

activityNew$wd <- wd
```

Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).

```{r echo = TRUE}
table3 <- aggregate(activityNew$steps~activityNew$interval+activityNew$wd,
          data=activityNew,
          FUN=mean)
colnames(table3) <- c("interval","wd","steps")


library(lattice)
xyplot(steps~interval | wd, 
       table3, 
       layout=c(1,2),
       type="l", 
       xlab="Interval", 
       ylab="Number of steps")
```
